Fish & Benthic Community data: Antigua, Barbuda, & Bonaire - Aug. 2017

### 2018-11-24 r/Data_prodding.Rmd
11/24

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(startR)
library(here)
library(tidyverse)
library(corrplot)
library(ggplot2)
library(RColorBrewer)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(car)
library(nlme)
library(gamm4)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  filter(length_cm>=15)
sum_site_sp_ph <- read.csv(here("data","sum_site_sp_ph.csv"), stringsAsFactors=F) %>%
  select(-X) 
```

@@

First, check distribution of predictor variables of interest: not very normally distributed...
```{r,warning=FALSE,echo=FALSE}
pred <- sum_site %>% 
  select(tot_bm,tot_den,scar_bm,scar_den,carn_bm,carn_den,
         cca_cover,lc_cover,ma_cover,ma_canopy,ta_cover,ta_canopy,rugosity) %>% 
  gather() %>% 
  na.omit()

@@

```{r,echo=FALSE}
pred <- sum_id %>% select(tot_bm,tot_den,scar_bm,scar_den,consp_bm,consp_den,
                           carn_bm,carn_den,cca_cover,lc_cover,
                           ma_cover, ma_canopy,ta_cover,ta_canopy,rugosity)
c = cor(pred, use="pairwise.complete.obs")
corplot <- corrplot(c, type = "upper", order = "hclust")
```

@@

```{r}
pca_pred <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              select(ma_ind,ta_cover,ta_canopy,lc_cover,rugosity,scar_den,scar_bm,)), 
  center = T,scale = T)

@@

```{r}
pca_bent <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              select(ma_ind,ta_cover,ta_canopy,lc_cover,rugosity,)), 
  center = T,scale = T)

summary(pca_bent)
plot(pca_bent,type="l")

autoplot(pca_bent, data = sum_site, colour = 'island',
         # frame = T, frame.type = "norm",
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(name="island", values=c("lightblue", "darkseagreen", "lightsalmon")) + 
    theme(legend.direction = 'horizontal', legend.position = 'top') +
    theme_minimal()

# add PC1 and PC2 as variables in dataset
sum_site_pca1 <- sum_site %>% 
  bind_cols(as.data.frame(pca_bent$x) %>% 
           select(PC1,PC2)) %>%
  janitor::clean_names(case="old_janitor")
sum_id_pca1 <- sum_id %>% left_join(select(sum_site_pca1,site,pc1,pc2), by = "site")
sum_ssp_pca1 <- sum_site_sp_ph %>% left_join(select(sum_site_pca1,site,pc1,pc2), by = "site")
write.csv(sum_id_pca1,file=here("data/sum_id_pca1.csv"))
write.csv(sum_ssp_pca1,file=here("data/sum_ssp_pca1.csv"))
```

@@

```{r}
ggplot(filter(sum_id_pca1, species_code != "rbp" & island != "Barbuda" & length_cm>=16 & length_cm<=24), aes(x = ma_ind,y=fr)) +
  facet_grid(.~species) +
  geom_smooth(method="loess") +
  geom_point(shape=18) +
  labs(y="Feeding rate (bites/hr)", x="Macroalgal index", title = "Hourly feeding rate") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
lme_fr <- lme(fr~phase+length_cm+species+scar_bm+pc1+pc2,
              data=filter(sum_id_pca1, species_code!="rbp"),
              random=~1|site, 
              na.action = na.omit
              )
summary(lme_fr)
vif(lme_fr) # test VIF here, because I'm not sure how to do it in GAMM yet...? All low VIF (<3) when random = island, but when random = site, VIFs jump up (for scarid_den & pc2)
```

@@

```{r,eval=F}
gamm<-gamm(fr~phase+s(length_cm)+s(pc1)+s(pc2)+s(scar_bm)+s(scar_den), 
           family=gaussian(link=identity),
           data=filter(sum_id_pca1, species_code=="stop"),
           random=list(site=~1),
           method="REML"
           )
summary(gamm$gam)
plot(gamm$gam,pages=1)
```
```{r,eval=F}
gamm<-gamm(fr_mean~phase+species+s(pc1)+s(pc2)+s(scar_bm)+s(scar_den), 
           family=gaussian(link=identity),
           data=filter(sum_ssp_pca1, species_code!="rbp" & island!="Barbuda"),
           random=list(site=~1),
           method="REML"
           )
summary(gamm$gam)
plot(gamm$gam,pages=1)
```

>>>>

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(startR)
library(here)
library(tidyverse)
library(corrplot)
library(ggplot2)
library(RColorBrewer)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(car)
library(nlme)
library(gamm4)
library(xtable)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  filter(length_cm>=15)
sum_site_sp_ph <- read.csv(here("data","sum_site_sp_ph.csv"), stringsAsFactors=F) %>%
  select(-X) 
fish <- read.csv(here("data","fish.csv"), stringsAsFactors=F) %>%
  select(-X) 
```

@@

First, check distribution of predictor variables of interest: not very normally distributed...
```{r,warning=FALSE,echo=FALSE}
pred <- sum_site %>% 
  select(tot_bm,tot_den,scar_bm,scar_den,carn30_bm,carn30_den,
         cca_cover,lc_cover,ma_cover,ma_canopy,ta_cover,ta_canopy,rugosity,spear_daily) %>% 
  gather() %>% 
  na.omit()

@@

```{r,echo=FALSE}
pred <- sum_id %>% select(tot_bm,tot_den,scar_bm,scar_den,consp_bm,consp_den,
                           carn30_bm,carn30_den,cca_cover,lc_cover,
                           ma_cover, ma_canopy,ta_cover,ta_canopy,rugosity)
c = cor(pred, use="pairwise.complete.obs")
corplot <- corrplot(c, type = "upper", order = "hclust")
```

@@

```{r}
pca_pred <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              select(ma_ind,ta_cover,ta_canopy,lc_cover,rugosity,scar_den,scar_bm,spear_daily)),
  center = T,scale = T)

@@

```{r}
pca_all <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              # filter(island!="Barbuda") %>%
              select(ma_cover, ma_canopy, ta_cover, ta_canopy, rugosity, scar_bm, scar_den)),
  center = T,scale = T)

autoplot(pca_all, data = sum_site, colour = 'island',
         # frame = T, frame.type = "norm",
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(name="island", values=c("lightblue", "darkseagreen", "lightsalmon")) + 
    theme(legend.direction = 'horizontal', legend.position = 'top') +
    theme_minimal()

pca_bent <- prcomp(na.omit(sum_site %>% 
              remove_rownames %>% 
              column_to_rownames(var="site") %>%
              select(ma_ind,ta_cover,ta_canopy,lc_cover,rugosity)), 
  center = T,scale = T)
summary(pca_bent)
plot(pca_bent,type="l")

# add PC1 and PC2 as variables in dataset
sum_site <- sum_site %>% 
  # filter(island!="Barbuda") %>%
  bind_cols(as.data.frame(pca_bent$x) %>% 
           select(PC1,PC2)) %>%
  rename(pc1_bent=PC1,
         pc2_bent=PC2) %>% 
  bind_cols(as.data.frame(pca_all$x) %>% 
           select(PC1,PC2)) %>%
  rename(pc1_all=PC1,
         pc2_all=PC2)

sum_id_pca <- sum_id %>% 
  left_join(select(sum_site,site,pc1_bent,pc2_bent,pc1_all,pc2_all), by = "site")

```

@@

```{r}
ggplot(filter(sum_id_pca, species_code != "rbp" & island != "Barbuda" & length_cm>=16 & length_cm<=24), aes(x = ma_ind,y=fr)) +
  facet_grid(.~species) +
  geom_smooth(method="loess") +
  geom_point(shape=18) +
  labs(y="Feeding rate (bites/hr)", x="Macroalgal index", title = "Hourly feeding rate") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r}
lme_fr <- lme(fr~phase+length_cm+species+scar_bm+pc1_bent+pc2_bent,
              data=filter(sum_id_pca, species_code!="rbp"),
              random=~1|island, # do I need random slope too?
              na.action = na.omit
              )
summary(lme_fr)
vif(lme_fr) # test VIF here, because I'm not sure how to do it in GAMM yet...? All low VIF (<3) when random = island, but when random = site, VIFs jump up (for scarid_den & pc2)
```

@@

```{r,eval=F}
gamm<-gamm(fr~phase+s(length_cm)+s(pc1_bent)+s(pc2_bent)+s(scar_bm)+s(scar_den), 
           family=gaussian(link=identity),
           data=filter(sum_id_pca, species_code=="qup"),
           random=list(site=~1),
           method="REML"
           )
summary(gamm$gam)
plot(gamm$gam,pages=1)
```
```{r,eval=F}
gamm1<-gamm(fr_mean~phase+species+s(pc1_bent)+s(pc2_bent)+s(scar_bm)+s(scar_den), 
           family=gaussian(link=identity),
           data=filter(sum_ssp_pca, species_code!="rbp" & island!="Barbuda"),
           random=list(site=~1),
           method="REML"
           )
summary(gamm1$gam)
AIC(gamm1$lme)
plot(gamm1$gam,pages=1)

```

### 2018-11-24 r/Follows.Rmd
11/24

follows <- read.csv(here("data", "follows.csv"), strip.white = T, stringsAsFactors = F) %>%
  janitor::clean_names(case = "old_janitor") %>%
  filter(date != "" & date != "3/26/17") %>% 
  select(-activity_code) %>% 
  unite("id",c(site,diver,date,time,follow_number),sep="_", remove=FALSE) %>%
  mutate(
    time_sec = as.numeric(time_sec),
    time_frac = as.numeric(time_fraction),
    length_cm = as.numeric(length_cm),
    weight_g=as.numeric(weight_g),
    bites = as.numeric(ifelse(is.na(bites),0,bites))
  ) %>%
  replace(. =="#N/A", NA)

@@

### 1_3 Join datasets, print .csv
```{r, echo=FALSE,message=FALSE,warning=FALSE}
# integrate all site-level variables
sum_site <- sum_site %>% 
  left_join(site, by="site")
sum_id <- sum_id %>% 
  left_join(site, by="site") %>%
  left_join(sp_site, by=c("species","site")) # add conspecific scarid info (based on site/species)
sum_site_sp_ph <- sum_site_sp_ph %>% 
  left_join(site, by="site") %>%
  left_join(sp_site, by=c("species","site")) # add conspecific scarid info (based on site/species)

>>>>

follows <- read.csv(here("data", "follows.csv"), strip.white = T, stringsAsFactors = F) %>%
  janitor::clean_names(case = "old_janitor") %>%
  filter(date != "" & date != "3/26/17") %>% 
  select(-activity_code) %>% 
  unite("id",c(site,diver,date,time,follow_number),sep="_", remove=FALSE) %>%
  mutate(
    time_sec = as.numeric(time_sec),
    time_frac = as.numeric(time_fraction),
    length_cm = as.numeric(length_cm),
    weight_g=as.numeric(weight_g),
    bites = as.numeric(ifelse(is.na(bites),0,bites))
  ) %>%
  replace(. =="#N/A", NA) %>%
  filter(length_cm >= 15)

@@

### 1_3 Join datasets, print .csv
```{r, echo=FALSE,message=FALSE,warning=FALSE}
# integrate all site-level variables
sum_site <- sum_site %>% 
  left_join(site, by=c("island","site"))
sum_id <- sum_id %>% 
  left_join(site, by=c("island","site")) %>%
  left_join(sp_site, by=c("species","site")) # add conspecific scarid info (based on site/species)
sum_site_sp_ph <- sum_site_sp_ph %>% 
  left_join(site, by=c("island","site")) %>%
  left_join(sp_site, by=c("species","site")) # add conspecific scarid info (based on site/species)

### 2018-11-24 r/SEM.Rmd
11/24

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
library(tidyr)
library(lavaan)
library(semPlot)
```

@@

```{r}
# define model pathways
qup_df <- sum_id %>% 
  select(scar_bm, ma_cover, ta_cover, fr, g_frac, rugosity, int_scar, length_cm, lc_cover) %>% 
  na.omit()

sem <- '
  # latent variable indicators  
      risk =~ scar_bm + rugosity
      nutrition =~ ma_cover + ma_canopy + ta_cover + ta_canopy
  # regressions
      fr ~ length_cm + risk + nutrition
      rugosity ~ lc_cover
      lc_cover ~ ma_cover + ta_cover
      ta_cover ~ scar_bm
      ma_cover ~ scar_bm
'

sem1 <- '
  # latent variable indicators
      nutrition =~ ma_cover + ta_cover
  # regressions
      fr ~ length_cm + nutrition
      lc_cover ~ ma_cover + ta_cover
'

fit <- sem(sem1, data=qup_df)
varTable(fit)
summary(fit, standardized=T, fit.measures=T,rsq=T)
semPaths(fit)
fitMeasures(fit, c("cfi","rmsea","srmr"))
```

>>>>

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
library(here)
library(tidyverse)
library(lavaan)
library(semPlot)
```

@@

```{r}
# define model pathways
sem_full <- '
  # latent variable indicators
      risk =~ scar_bm_sc + rugosity_sc
      nutrition =~ ma_cover + ma_canopy + ta_cover + ta_canopy
  # regressions
      fr_sc ~ length_cm + risk + nutrition
      rugosity_sc ~ lc_cover
      lc_cover ~ ma_cover + ma_canopy + ta_cover + ta_canopy
      ta_cover ~ scar_bm_sc
      ma_cover ~ scar_bm_sc    
      ta_canopy ~ scar_bm_sc
      ma_canopy ~ scar_bm_sc 
'
```

```{r}
# testing partial SEMs

sem_df <- sum_id %>% 
  filter(island!="Barbuda") %>%
  select(fr, g_frac, species_code, phase, scar_bm, scar_den, carn30_bm, tot_bm, spear_daily, ma_cover, ma_canopy, ta_cover, ta_canopy, rugosity, int_scar, length_cm, lc_cover) %>% 
  mutate(phase_dum=ifelse(phase=="i",1,2),
         fr_sc = fr/100,
         scar_bm_sc = scar_bm/100,
         rugosity_sc = rugosity*10) %>%
  na.omit()
vet_df <- sem_df %>% filter(species_code=="qup")
vir_df <- sem_df %>% filter(species_code=="stop")

sem1 <- '
  # latent variable indicators
      risk =~ scar_bm_sc
      nutrition =~ ma_cover + ta_cover
  # regressions
      fr_sc ~ length_cm + phase_dum + nutrition + risk
'

sem2 <- '
  # latent variable indicators
      risk =~ scar_bm_sc + scar_den + rugosity_sc + spear_daily
      nutrition =~ ma_cover + ta_cover
  # regressions
      fr_sc ~ length_cm + phase_dum + nutrition + risk
      rugosity_sc ~ lc_cover
      lc_cover ~ ma_cover + ta_cover
'

sem3 <- '
  # latent variable indicators
      risk =~ scar_bm_sc + scar_den + spear_daily
      nutrition =~ ma_cover + ta_cover
  # regressions
      fr_sc ~ length_cm + phase_dum + nutrition + risk
      lc_cover ~ ma_cover + ta_cover
'

fit <- sem(sem3, data=vet_df, missing="ML", std.lv=T, orthogonal=T)
varTable(fit)
summary(fit, standardized=T, fit.measures=T, rsq=T)
semPaths(fit)
fitMeasures(fit, c("cfi","rmsea","srmr"))
```

### 2018-11-24 r/Sites.Rmd
11/24

fish_site <-fish_tran %>% 
  group_by(site) %>% 
  summarize(
    n=n(), 
    tot_bm=mean(bm_t), 
    tot_bm_se=(sd(bm_t))/sqrt(n), 
    tot_den=mean(den_t), 
    tot_den_se=(sd(den_t))/sqrt(n), 
    tot_l=mean(l_t), 
    tot_l_se=(sd(l_t))/sqrt(n)
    ) %>% 
  select(-n) # average across transects within each site

boxplot(bm_t~site, las=2, data = fish_tran)
```

## Total fish populations, by species and site
```{r,message=F,warning=F}
# Because not all species were present at each site/transect, I need to create template to add 0 values for biomass and density in transects where they are absent.
exp_tran <- fish %>% 
  group_by(site,transect) %>% 
  summarize() # all possible site/transect combinations
exp_sp <- fish %>% tidyr::expand(nesting(species,family),site) # all possible species/site combinations
template_sp <- full_join(exp_sp,exp_tran,by="site") # species/site/transect combinations

@@

## Total fish populations, by functional group and site
```{r,message=F,warning=F}
# Herbivores
herb_tran<- fish %>% 
  filter(family %in% c("Scaridae","Acanthuridae"),
         biomass != 0) %>% 
  group_by(site,transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran, by=c("site","transect")) %>% # join with transect-level template
  mutate_each(funs(replace(.,is.na(.),0)), -l_t) # missing biomass and density values should be 0

@@

acan_tran <- fish %>% 
  filter(family=="Acanthuridae",
         biomass != 0) %>% 
  group_by(site,transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>%
  right_join(exp_tran, by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

@@

# Carnivores
carn_tran <- fish %>% 
  filter(family %in% c("Serranidae","lutjanidae","Carangidae"),
         biomass != 0) %>% 
  group_by(site,transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran,by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

@@

@@

# Integrating and exporting .csvs
```{r, echo=F,message=F,warning=F}
site <- fish_site %>% 
  left_join(herb_site,by="site") %>% 
  left_join(acan_site,by="site") %>% 
  left_join(scar_site,by="site") %>% 
  left_join(scar_site_sp,by="site") %>% 
  left_join(scar_site_ph,by="site") %>% 
  left_join(carn_site,by="site") %>%
  left_join(bent_site,by="site") %>%
  left_join(human,by="site")

>>>>

fish_site <-fish_tran %>% 
  group_by(site, island) %>% 
  summarize(
    n=n(), 
    tot_bm=mean(bm_t), 
    tot_bm_se=(sd(bm_t))/sqrt(n), 
    tot_den=mean(den_t), 
    tot_den_se=(sd(den_t))/sqrt(n), 
    tot_l=mean(l_t), 
    tot_l_se=(sd(l_t))/sqrt(n)
    ) %>% 
  select(-n) %>% # average across transects within each site\
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)

ggplot(fish_site,
      aes(x=factor(site, levels = fish_site$site), y=tot_bm)) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        geom_errorbar(aes(ymin=tot_bm-tot_bm_se, ymax=tot_bm+tot_bm_se),
                  width=.2,
                  position=position_dodge(.9)) +
        scale_fill_manual(values = c("gray", "slategray2", "darkseagreen")) +
        labs(title="Total fish biomass") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Total fish populations, by species and site
```{r,message=F,warning=F}
# Because not all species were present at each site/transect, I need to create template to add 0 values for biomass and density in transects where they are absent.

exp_tran <- fish %>% 
  group_by(site,transect) %>% 
  summarize()  # all possible site/transect combinations
exp_sp <- fish %>% tidyr::expand(nesting(species,family),site) # all possible species/site combinations
template_sp <- full_join(exp_sp,exp_tran,by="site") # species/site/transect combinations

@@

## Total fish populations, by functional group and site
```{r,message=F,warning=F}
island_site <- fish_site %>% select(island,site) # island/site relationships to add to plots

# Herbivores
herb_tran<- fish %>% 
  filter(family %in% c("Scaridae","Acanthuridae"),
         biomass != 0) %>% 
  group_by(site, transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran, by=c("site","transect")) %>% # join with transect-level template
  mutate_each(funs(replace(.,is.na(.),0)), -l_t) # missing biomass and density values should be 0

@@

acan_tran <- fish %>% 
  filter(family=="Acanthuridae",
         biomass != 0) %>% 
  group_by(site, transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>%
  right_join(exp_tran, by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

@@

# Carnivores
carn_tran <- fish %>% 
  filter(family %in% c("Serranidae", "Lutjanidae", "Carangidae", "Sphyraenidae", "Haemulidae"),
         biomass != 0) %>% 
  group_by(site, transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran,by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

@@

# Carnivores over 30cm
carn30_tran <- fish %>% 
  filter(family %in% c("Serranidae","Lutjanidae","Carangidae", "Sphyraenidae", "Haemulidae"),
         biomass != 0, length>=30) %>% 
  group_by(site, transect) %>% 
  summarize(
    bm_t=sum(biomass)/1.2,
    den_t=n()/1.2,
    l_t=mean(length)
    ) %>% 
  right_join(exp_tran,by=c("site","transect")) %>%
  mutate_each(funs(replace(.,is.na(.),0)), -l_t)

carn30_site<-carn30_tran %>% 
  group_by(site) %>% 
  summarize(
    n=n(),
    l_n=sum(!is.na(l_t)),
    carn30_bm=mean(bm_t),
    carn30_bm_se=(sd(bm_t))/sqrt(n),
    carn30_den=mean(den_t),
    carn30_den_se=(sd(den_t))/sqrt(n),
    carn30_l=mean(l_t, na.rm = T),
    carn30_l_se=(sd(l_t, na.rm = T))/sqrt(l_n)
    ) %>% 
  select(-c(n,l_n)) %>%
  replace(. == "NaN",NA)

ggplot(right_join(carn30_site, island_site, by="site"),
      aes(x=factor(site, levels = fish_site$site), y=carn30_bm)) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        geom_errorbar(aes(ymin=carn30_bm-carn30_bm_se, ymax=carn30_bm+carn30_bm_se),
                      width=.2,
                      position=position_dodge(.9)) +
        scale_fill_manual(values = c("gray", "slategray2", "darkseagreen")) +
        labs(title="Biomass of Piscivores over 25cm") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# Integrating and exporting .csvs
```{r, echo=F,message=F,warning=F}
site <- fish_site %>% 
  left_join(herb_site,by="site") %>% 
  left_join(acan_site,by="site") %>% 
  left_join(scar_site,by="site") %>% 
  left_join(scar_site_sp,by="site") %>% 
  left_join(scar_site_ph,by="site") %>% 
  left_join(carn_site,by="site") %>%
  left_join(carn30_site,by="site") %>%
  left_join(bent_site,by="site") %>%
  left_join(human,by="site")
